\chapter{Kernel Smoothing Methods}
\label{ch:6}

\begin{exercise}
  For Gaussian kernel, since $K_{\lambda}(x_0,x_i)$ is differentiable w.r.t.
  $x_0$, we have
  \begin{align}
    \dv{\hat{f}(x_0)}{x_0} &= \frac{\left(\sum_{i=1}^Ny_iK'_{\lambda}(x_0,
    x_i)\right) \left(\sum_{i=1}^NK_{\lambda}(x_0,
    x_i)\right) - \left(\sum_{i=1}^NK'_{\lambda}(x_0,
    x_i)\right)\left(\sum_{i=1}^Ny_iK'_{\lambda}(x_0,
    x_i)y_i\right)} {\left(\sum_{i=1}^NK_{\lambda}(x_0,
    x_i)\right)^2}
  \end{align}
  
  Since Epanechnikov kernel is not differentiable, the corresponding
  Nadaraya-Watson kernel smooth function is not differentiable, either.
\end{exercise}

\begin{exercise}
  Denote $\mathbf{l}(x_0) = [l_1(x_0),\ldots,l_N(x_0)]^T$ as a $N$-by-1 vector.
  From Eq. (6.8) we can see that
  \begin{align}
    \mathbf{l}^T(x_0) &= \mathbf{b}(x_0)^T
    \left(\mathbf{B}^T\mathbf{W}(x_0)\mathbf{B}\right)^{-1}
    \mathbf{B}^T\mathbf{W}(x_0)
  \end{align}
  therefore
  \begin{align}
    \mathbf{l}^T(x_0)\mathbf{B} &= \left[\sum_{i=1}^Nl_i(x_0),\ldots,
    \sum_{i=1}^Nl_i(x_0)x_i^{k}\right] \notag\\
    &= \mathbf{b}^T(x_0) = [1, \ldots, x_0^{k}]
  \end{align}
  which suggests that 
  \begin{align}
    \sum_{i=1}^Nl_i(x_0)x_i^{j} = x_0^j,\,j=0.\ldots,k
  \end{align}
  \begin{itemize}
    \item When $j=0$, we have $\sum_{i=1}^Nl_i(x_0) = 1$.
    \item When $j>0$, since 
    \begin{align}
      \sum_{i=1}^Nl_i(x_0)x_i^{j} &= x_0^j  = x_0^l\cdot x_0^{j-l} =
      \sum_{i=1}^Nl_i(x_0)x_i^{l}x_0^{j-l}
    \end{align}
    for any $0\leq l\leq j$, it is easy to verify that 
    \begin{align}
      \sum_{i=1}^Nl_i(x_0)(x_i - x_0)^j = 0.
    \end{align}
    which suggests that the bias is 0 to order $k$ according to Eq. (6.10). 
  \end{itemize}
  
\end{exercise}

\begin{exercise}
  ???
\end{exercise}

\begin{exercise}
  The Mahalanobis choice of $\mathbf{A} = \mathbf{\Sigma}^{-1}$ has the effect
  of ``eqaulizaing'' the distance measure in each dimension according to how the
  data vary over that dimension, while $\mathbf{A} = \mathbf{I}$ results in the
  Euclidean distance which ignores the distribution of the data $\mathbf{X}$.
  
  A kernel that downweightshigh-frequency components in the
  distance metric can be constructed as $\mathbf{A} = \mathbf{F}^T\mathbf{F}$,
  where the rows of $\mathbf{F}$ are the cyclic-shifted version of a low-pass
  filter. In this way, $\mathbf{Fx}$ represents the circular convolution of the
  filter and the samples $\mathbf{x}$ which rejects high frequency components.
  To ignore high-frequency components completely, we can simply define
  $\mathbf{F}$ as a all-1 matrix.
\end{exercise}

\begin{exercise}
  Denote the binary response indicator vector for the $i$-th record as
  $\mathbf{y}_i$, such that $y_{ij}=1$ if $g_i=j$ and otherwise $y_{ij}=0$,
  $j=1,\ldots,J$. Then the local log-likelihood can be rewritten as
  \begin{align}
    l(\bm{\beta}) &= \sum_{i=1}^N K_{\lambda}(x_0, x_i)
    \left[\sum_{j=1}^{J-1}y_{ij}\log\mbox{Pr}(G=j|X=x_i)  +
    \left(1-\sum_{j=1}^{J-1}y_{ij}\right) \log\mbox{Pr}(G=J|X=x_i) \right]
    \notag\\ &=
    \sum_{i=1}^N K_{\lambda}(x_0, x_i)
    \left[\sum_{j=1}^{J-1}y_{ij}\beta_{j0}(x_0)
    -\log\left(1+\sum_{j=1}^{J-1} \exp(\beta_{j0}(x_0)) \right) \right]
  \end{align} 
  To maximize the log-likelihood, setting the derivative w.r.t $\beta_{j0}$ to 0
  results in
  \begin{align}
    \pdv{l(\bm{\beta})}{\beta_{j0}(x_0)} = \sum_{i=1}^N K_{\lambda}(x_0,
    x_i)\left(y_{ij} - p_j\right) = 0
  \end{align}
  where
  \begin{align}
    p_j &= \frac{\exp(\beta_{j0}(x_0))}{1 + \sum_{k=1}^{J-1}
    \exp(\beta_{k0}(x_0))}
  \end{align}
  therefore $\beta_{j0}, j=1,\ldots,J-1$ should be selected such that
  \begin{align}
    p_j &= \frac{\sum_{i=1}^N K_{\lambda}(x_0,x_i)y_{ij}} {\sum_{i=1}^N
    K_{\lambda}}
  \end{align}
  which amounts to smoothing the binary response indicators for each class
  separately using a Nadaraya–Watson kernel smoother with kernel weights
  $K_{\lambda}(x_0,x_i)$.
\end{exercise}

\begin{exercise}
  Divide the set of monomials into $Z$ and $X$. Define kernel on $Z$ and use
  $X$ as predictors. Given a new input $[\mathbf{z}_0, \mathbf{x}_0]$, fit local
  regression model as
  \begin{align}
    \min_{\alpha(\mathbf{z}_0),
    \bm{\beta}(\mathbf{z}_0)}\sum_{i=1}^NK_{\lambda}(\mathbf{z}_0,\mathbf{z}_i)
    (y_i-\alpha(\mathbf{z}_0) - \mathbf{x}_i^T\bm{\beta}(\mathbf{z}_0) )
  \end{align}
\end{exercise}

\begin{exercise}
  \begin{align}
    \frac{1}{N} \sum_{k=1}^N \sum_{i\not=k}
    K_{\lambda}(\mathbf{x}_i,\mathbf{x}_k) (y_i - \alpha_k -
    \mathbf{x}_i^T\bm{\beta}_k)
  \end{align}
\end{exercise}

\begin{exercise}
  The Parzen density estimate for $X, Y$ jointly and $X$ alone are
  \begin{subequations}
    \begin{align}
      \hat{f}_{X,Y}(x,y) & = \frac{1}{N}\sum_{i=1}^N
      \phi_{\lambda}(x-x_i)\phi_{\lambda}(y-y_i) \\
      \hat{f}_{X}(x) & = \frac{1}{N}\sum_{i=1}^N
      \phi_{\lambda}(x-x_i)
    \end{align}
  \end{subequations}
  respectively, therefore
  \begin{align}
    \mathbb{E}[Y|X] &= \int y \frac{\hat{f}_{X,Y}(x,y)}{\hat{f}_{X}(x)}dy
    \notag\\ &=
    \frac{\sum_{i=1}^N \phi_{\lambda}(x-x_i) \int y\phi_{\lambda}(y-y_i)dy}
    {\sum_{i=1}^N\phi_{\lambda}(x-x_i)}
  \end{align}
  which is a Nadaraya-Watson estimator. 
  
  For classification we adopt the
  product kernel $\phi_{\lambda}(X)\delta(g)$, where $\delta(\cdot)$ is the
  Kronecker delta function. As a result, the Parzen density estimate for $X, G$
  jointly is
  \begin{align}
    \hat{f}_{X,G}(x,g) & = \frac{1}{N}\sum_{i=1}^N
    \phi_{\lambda}(x-x_i)\delta(g=g_i)
  \end{align}
  therefore the probability estimation is
  \begin{align}
    \mbox{Pr}(G=g|X=x) = \frac{\hat{f}_{X,G}(x,g)} {\hat{f}_{X}(x)} =
    \frac{\sum_{g_i=g}\phi_{\lambda}(x-x_i)} {\sum_{i=1}^N\phi_{\lambda}(x-x_i)}
  \end{align}
\end{exercise}

\begin{exercise}
  Naive bayesian model makes a stronger assumption that given a class $G = j$
  the features $X_k$ are independent as in Eq. (6.27), which leads to the
  additive form of the log-likelihood function in Eq. (6.27)  On the contrary
  the GAM model directly assumes a additive form of the log-likelihood function
  (Eq. (9.8)) and no specific form of the distribution function is assumed.
  
  Naive bayesian model enables the estimation of the 1-D density function of the
  features conditioned on class $f_{jk}$ , while in the GAM model the additive
  components $f_1,\ldots, f_p$ are estimated by a iterative backfitting
  algorithm.
\end{exercise}

\begin{exercise}
  \begin{align}
    \mathbb{E}\left[\mbox{ASR}(\lambda)\right] & = \frac{1}{N}
    \mathbb{E}\left[ \|\mathbf{y} - \mathbf{S}_{\lambda}\mathbf{y}\|^2\right]
    \notag\\
    &= \frac{1}{N}\mathbb{E}\left[\|(\mathbf{f} + \bm{\epsilon}) -
    \mathbf{S}_{\lambda}(\mathbf{f} + \bm{\epsilon})\|^2 \right] \notag\\
    &= \frac{1}{N} \|\mathbf{f} - \mathbf{S}_{\lambda}\mathbf{f}\|^2 +
    \frac{1}{N} \mathbb{E}\left[\|\bm{\epsilon} -
    \mathbf{S}_{\lambda}\bm{\epsilon})\|^2 \right] \notag \\
    &= \frac{1}{N} \|\mathbf{f} - \mathbf{S}_{\lambda}\mathbf{f}\|^2 +
    \frac{\left[N - 2\mbox{tr}(\mathbf{S}_{\lambda}) +
    \mbox{tr}(\mathbf{S}_{\lambda}\mathbf{S}_{\lambda}^T)\right]\sigma^2}{N}
  \end{align}
  \begin{align}
    \mbox{PE}(\lambda) & = \frac{1}{N}\mathbb{E}\left[\|\mathbf{y}^* -  
    \mathbf{S}_{\lambda}\mathbf{y}\|^2 \right] \notag\\
    &= \frac{1}{N}\mathbb{E}\left[\|(\mathbf{f} + \bm{\epsilon}^*) -
    \mathbf{S}_{\lambda}(\mathbf{f} + \bm{\epsilon})\|^2 \right] \notag\\
    &= \frac{1}{N} \|\mathbf{f} - \mathbf{S}_{\lambda}\mathbf{f}\|^2 +
    \frac{1}{N} \mathbb{E}\left[\|\bm{\epsilon}^* -
    \mathbf{S}_{\lambda}\bm{\epsilon})\|^2 \right] \notag \\
    &= \frac{1}{N} \|\mathbf{f} - \mathbf{S}_{\lambda}\mathbf{f}\|^2 +
    \frac{\left[N +
    \mbox{tr}(\mathbf{S}_{\lambda}\mathbf{S}_{\lambda}^T)\right]\sigma^2}{N}
  \end{align}
  therefore
  \begin{align}
    \mbox{PE}(\lambda) & =  \mathbb{E}\left[\mbox{ASR}(\lambda)\right] +
    \frac{2\mbox{tr}(\mathbf{S}_{\lambda})\sigma^2}{N} =
    \mathbb{E}\left[ C_{\lambda}\right]
  \end{align}
\end{exercise}

\begin{exercise}
  The likelihood is maximized to $+\infty$ by setting any $\bm{\mu}_m$ to a
  record $\mathbf{x}_i$ and setting $\mathbf{\Sigma} = \mathbf{0}$.
\end{exercise}

\begin{exercise}[(Program)]
\end{exercise}
